\documentclass[apjpt4]{aastex}
\usepackage{fullpage}
\usepackage[small,compact]{titlesec}
\usepackage{fancyhdr}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\pagestyle{fancy}

\renewcommand{\headrulewidth}{0pt}
\topmargin=-24pt
\headheight=12pt
\headsep=12pt
\fancyhf{}

\setlength{\parindent}{0in}
%\chead{--\ \thepage\ --}

%Biographical Sketches (2 pages each; long collaborator lists may continue on a
%3rd page). Biographical Sketches are required for the PI and all co-PIs, and
%additional senior personnel at all participating institutions. See GPG for
%details.  

\begin{document}

\section*{\Large Biographical Sketch: Aaron Parsons}

%Biographical Sketch, not to exceed two (2) pages. See the Grant Proposal Guide
%or NSF Grants.gov Application Guide for format. The Biographical Sketch must
%clearly include all information necessary to certify the candidate's
%eligibility, including identification of U.S.  citizenship or permanent
%resident status, as well as all components described in the Grant Proposal
%Guide or NSF Grants.gov Application Guide.

\subsection*{Education/Professional Preparation}
\vspace{-8pt}

%A list of the individual's undergraduate and graduate education and postdoctoral training as indicated below:
%Undergraduate Institution(s) Major Degree & Year
%Graduate Institution(s) Major Degree & Year
%Postdoctoral Institution(s) Area Inclusive Dates (years)

\begin{tabular}{ll}
(2009--\hfill)& U. of California, Berkeley (UCB).  NSF Astronomy and
Astrophysics Postdoctoral Fellow\\
(2009--\hfill)& UCB Space Sciences Laboratory (SSL).  Honorary Townes Postdoctoral Fellow\\
(2004--2009)& UCB.  Ph.D. Astrophysics\\
(1998--2002)& Harvard U.  Double B.A. Physics and Mathematics\\
\end{tabular}

\subsection*{Appointments}
\vspace{-8pt}

%A list, in reverse chronological order, of all the individual's
%academic/professional appointments beginning with the current appointment.

\begin{tabular}{ll}
\vspace{-2pt}
(2009--\hfill) &NSF Astronomy and Astrophysics Postdoctoral Fellowship, UCB\\
(2009--\hfill) &Honorary Townes Postdoctoral Fellowship, SSL\\
(2007--2009) &NAIC Pre-Doctoral Researcher, Arecibo Observatory, PR\\
(2005--2009)& Graduate Student Researcher,  UCB\\
(2002--2004)& Junior Development Engineer, SSL\\
\end{tabular}

\subsection*{Publications Most Closely Related to Project}
\vspace{-8pt}

%A list of: (i) up to 5 publications most closely related to the proposed project; and (ii) up to 5 other significant publications, whether or not related to the proposed project. Each publication identified must include the names of all authors (in the same sequence in which they appear in the publication), the article and journal title, book title, volume number, page numbers, and year of publication. If the document is available electronically, the website address also should be identified.
%
%For unpublished manuscripts, list only those submitted or accepted for
%publication (along with most likely date of publication). Patents, copyrights
%and software systems developed may be substituted for publications. Additional
%lists of publications, invited lectures, etc., must not be included. Only the
%list of 10 will be used in the review of the proposal.

%XXX update
Parsons, A.,  D. Backer, R. Bradley, J. Aguirre, E. Benoit, C. Carilli, G. Foster, N. Gugliucci, D. Herne, D. Jacobs, M. Lynch, J. Manley, C. Parashare, D. Werthimer, M. Wright.
``The Precision Array for Probing the Epoch of Re-ionization: Eight Station Results,''
{\it Astronomical Journal}, 139, 1468-1480, April 2010.

Parsons, A., D. Backer.
``Calibration of Low-Frequency, Wide-Field Radio Interferometers Using Delay/Delay-Rate Filtering''
{\t Astronomical Journal}, 138, 1, 219-226. July 2009.

Parsons, A., D. Backer, H. Chen, P. Droz, T. Filiba, D. MacMahon, J. Manley,
P. McMahon, A. Parsa, A. Siemion, D. Werthimer, M. Wright.
``A Scalable Correlator Architecture Based on Modular FPGA Hardware,
Reusable Gateware, and Data Packetization,''
{\it Publications of the Astronomical Society of the Pacific}, 120, 873, 1207-1221. November 2008.

Parsons, A., D. Backer, C. Chang, D. Chapman, H. Chen, P. Crescini, C. de Jesus,
C. Dick, P. Droz, D. MacMahon, K. Meder, J. Mock, V. Nagpal, B. Nikolic, 
A. Parsa, B. Richards, A. Siemion, J. Wawrzynek, D. Werthimer, M. Wright.
``PetaOp/Second FPGA Signal Processing for SETI and Radio Astronomy (Invited 
Paper),'' 
{\it Proc. Asilomar Conference on Signals and Systems, Pacific Grove, CA}. 
November 2006.

Parsons, A.
``The Symmetric Group in Data Permutation, with Applications to
a High-Bandwidth Streaming FFT Architecture,''
{\it IEEE Signal Processing Letters}.
16, 6, 477-480. June 2009.

\subsection*{Other Significant Publications}
\vspace{-8pt}

Parsons, A., D. Werthimer, D. Backer, T. Bastian, G. Bower, W. Brisken, H. Chen, A. Deller, T. Filiba, D. Gary, L. Greenhill, D. Hawkins, G. Jones, G. Langston, J. Lazio, J. van Leeuwen, D. Mitchell, J. Manley, A. Siemion, H. Kwok-Hay So, A. Whitney, D. Woody, M. Wright, K. Zarb-Adami
``Digital Instrumentation for the Radio Astronomy Community,''
{\it Astro2010 Decadal Survey White Paper in TEC: Technology Development},
http://arxiv.org/abs/0904.1181. April, 2009.

D. Backer, J. Aguirre, J. Bowman, R. Bradley, F. Briggs,
C. Carilli, S. Furlanetto, L. Greenhill, J. Hewitt,
C. Lonsdale, M. Morales, A. Parsons, S. Tingay, A. Whitney.
``HERA – Hydrogen Epoch of Reionization Arrays,''
{\it Astro2010 Decadal Survey White Paper in RMS: Radio and Millimeter/Submillimeter Facilites}, April, 2009.

Parsons, A., D. Backer, D. Werthimer, M. Wright.
``A New Approach to Radio Astronomy Signal Processing: Packet Switched, 
FPGA-based, Upgradeable, Modular Hardware and Reusable, Platform-Independent 
Signal Processing Libraries,'' 
{\it Proc. URSI Conference, Boulder, CO}.
January 2006.

Stanimirovi{\'c}, S. , M. Putman, C. Heiles, J. Peek, P. Goldsmith, B. Koo,
M. Kr{\v c}o, J. Lee, J. Mock, E. Muller, J. Pandian, A. Parsons, Y. Tang, D. Werthimer.
``First Results from the Arecibo Galactic H I Survey: The Disk/Halo Interface Region in the Outer Galaxy,''
{\it Astrophysical Journal}, 653, 1210-1225, Dec. 2006.

\subsection*{Synergistic Activities}
\vspace{-8pt}

%A list of up to five examples that demonstrate the broader impact of the
%individual’s professional and scholarly activities that focuses on the
%integration and transfer of knowledge as well as its creation. Examples could
%include, among others: innovations in teaching and training (e.g., development
%of curricular materials and pedagogical methods); contributions to the science
%of learning; development and/or refinement of research tools; computation
%methodologies, and algorithms for problem-solving; development of databases to
%support research and education; broadening the participation of groups
%underrepresented in science, mathematics, engineering and technology; and
%service to the scientific and engineering community outside of the individual’s
%immediate organization.

Developer of a cross-disciplinary undergraduate lab class focusing on the principles of radios, 
signal processing, and wireless communications.

Co-founder and advisory board member for the Collaboration for Astronomy
Signal Processing and Electronics Research (CASPER), which organizes the
development of open-source hardware and signal-processing libraries for community use.

Author of the open-source software toolkit ``Astronomical Interferometry in
PYthon'' (AIPY), with documentation and tutorials, which
provides a flexible environment for calibrating, imaging, and analysing interferometric data.

Creator and maintainer of ``AstroBaki,'' an online repository for public-domain
pedagogical materials such as lecture notes, laboratory
exercises, and homework problems.  Contributor of the foundational
set of lecture notes for introductory graduate astrophysics classes.

Volunteer science educator in local schools, focusing
on generating enthusiasm for science and inquisitiveness about natural
phenomena using hands-on demonstrations and activities.

\subsection*{Collaborators and Other Associations}
\vspace{-8pt}

%    * Collaborators and Co-Editors. A list of all persons in alphabetical order
%(including their current organizational affiliations) who are currently, or who
%have been collaborators or co-authors with the individual on a project, book,
%article, report, abstract or paper during the 48 months preceding the
%submission of the proposal. Also include those individuals who are currently or
%have been co-editors of a journal, compendium, or conference proceedings during
%the 24 months preceding the submission of the proposal. If there are no
%collaborators or co-editors to report, this should be so indicated.
%
%    * Graduate Advisors and Postdoctoral Sponsors. A list of the names of the
%individual’s own graduate advisor(s) and principal postdoctoral sponsor(s), and
%their current organizational affiliations.
%
%    * Thesis Advisor and Postgraduate-Scholar Sponsor. A list of all persons
%(including their organizational affiliations), with whom the individual has had
%an association as thesis advisor, or with whom the individual has had an
%association within the last five years as a postgraduate-scholar sponsor. The
%total number of graduate students advised and postdoctoral scholars sponsored
%also must be identified. 
%
%The information in section (e) above of the biographical sketch is used to help
%identify potential conflicts or bias in the selection of reviewers. See GPG
%Exhibit II-2 for additional information on potential reviewer conflicts.

James Aguirre [{\it U. of Pennsylvania}],
Donald Backer [{\it UCB}],
Richard Bradley [{\it U. of Virginia (UVA) and National Radio Astronomy Obs. (NRAO), Charlottesville}],
Chris Carilli [{\it NRAO, Socorro}],
%Chen Chang [{\it UCB}],
Henry Chen [{\it UCB}],
Daniel Chapman [{\it Columbia U.}],
%Patrick Crescini [{\it UCB}],
Chris Dick [{\it Xilinx Corp.}],
Pierre Droz [{\it UCB}],
Terry Filiba [{\it UCB}],
Griffin Foster [{\it Oxford}],
Nicole Gugliucci [{\it UVA}],
Dave Herne [{\it Curtin U.}],
Daniel Jacobs [{\it U. of Pennsylvania}],
%Christina de Jesus [{\it UCB}],
Merv Lynch [{\it Curtin U.}],
David MacMahon [{\it UCB}],
Jason Manley [{\it UCB}],
Erin Benoit [{\it NRAO, Charlottesville}],
Peter McMahon [{\it UCB}],
%Kirsten Meder [{\it UCB}],
%Jeff Mock [{\it UCB}],
Vinayak Nagpal [{\it UCB}],
Bora Nikolic [{\it UCB}],
Chaitali Parashare [{\it UVA}],
Arash Parsa [{\it UCB}],
Brian Richards [{\it UCB}],
Chris Salter [{\it Arecibo Obs.}],
Andrew Siemion [{\it UCB}],
Jonathan Wawrzynek [{\it UCB}],
Daniel Werthimer [{\it UCB}],
Melvyn Wright [{\it UCB}]

\subsection*{Advisors and Post-Doctoral Sponsors}
\vspace{-8pt}

Donald Backer [{\it UCB}],
Daniel Werthimer [{\it UCB}],
Chris Salter [{\it Arecibo Obs.}]


\end{document}
