\documentclass[onecolumn,11pt]{aastex}
%\usepackage{graphicx}
%\usepackage{fancyhdr}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\pagestyle{empty}
\linespread{1.0}

%Budget and Budget Justification, including budgets for any subawards.

\begin{document}
\begin{center}
{\bf \Large Budget Justification}
\end{center}

 University of California serves as the lead institution and provides technical, scientific and management support.

{\bf Personnel:} 
The personnel supported on this grant are located at the University of California, Berkeley Radio Astronomy Laboratory and Astronomy Department.

Aaron Parsons will serve as Principal Investigator and develop power spectrum algorithms and pipelines. We request funding for 1 month/year beginning in Year 2. The monthly rate for year 2 is projected to be \$11,011.

Dan Werthimer will serve as chief digital architect.  We request funding for 12 months/year at 20\%.  The monthly rate for year 1 is \$9463.

David DeBoer will serve as Project Manager/Project Engineer. We request funding for 12 months for all years, at 75\% in years 1-4 and 50\% in year 5. The monthly rate for year 1 is \$12,600.

David MacMahon will serve as R\&D Engineer for the digital system, including design, installation and support. We request funding for 12 months for all years, at 75\% in year 1-4, 25\% in year 5. The monthly rate for year 1 is \$8,859.

Matt Dexter will serve as R\&D Engineer for the digital system, including design, installation and support. We request funding for 12 months for all years, at 50\% in years 1 and 2, 75\% in years 3 and 4 and 25\% in year 5. The monthly rate for year 1 is \$8,859.

Calvin Cheng will serve as analog and digital technician, including design, installation and support. We request funding for 12 months for all years, at 10\% in years 1 and 5, 50\% in years 2 - 4. The monthly rate for year 1 is \$6,433.

Adrian Liu will provide post-doctoral algorithm design and implementation support.  We request funding for 12 months/year at 100\% for years 3-5.

We will hire two graduate student researchers. We request funding for 12 months/year at .4927 FTE. The monthly rate for year 1 is \$5,153.
Salary is increased at a rate of 2\% per year for academic staff, and 3.5\% per year for non-academic staff to allow for a cost of living adjustment.

We will hire one undergraduate support staff.  We request funding for 12 months/year at 25\% for all years.

\begin{table}
\centering
\label{tab:fringeBenefits}
Composite Fringe Benefit Rates
\begin{tabular}{| l | l | l | l | l | l |}
\hline
            ~ & FY15    & FY16    & FY17   & FY18   & FY19 \\ \hline \hline
Undergrad/GSR &	0\%     & 0\%     & 0\%    & 0\%    &  0\% \\ \hline
Staff         & 44.6\%  & 47.6\%  & 50.5\% & 51.3\% &  51.3\% \\ \hline
Academic      & 36.8\%  & 39.5\%  & 42.1\% & 42.6\% &   42.6\% \\ \hline
\hline
\end{tabular}
\end{table}


Rates beyond June 30, 2014, are estimates and are provided for planning purposes only. Future benefits rates are subject to review and approval by the Department of Health and Human Services on an annual or bi-annual basis. Therefore, regardless of which rates are used to estimate the cost of fringe benefits at the proposal stage, the fringe benefit costs ultimately charged to the sponsored project will always be based on the DHHS-approved fringe rates in existence at that time.

The Graduate Student Researchers will receive remissions of Fees, Health Insurance and Non-California Resident Tuition per semester at a rate of \$15,141 per semester in year one.  A 10\% per year escalation in fees are calculated.  Graduate Student fee remission, health insurance and non-California resident tuition remissions are not included in the Indirect Costs calculation. 

{\bf Equipment:}  As the managing institution, Berkeley will procure most of the South African deployed equipment for the project.  Funds are requested for the following pieces of equipment:
\begin{itemize}
\item {\em Year 1}:  Site relocation and HERA-37 construction.
\begin{itemize}
	\item antenna components, sub-assemblies and installation:  \$230k
	\item initial infrastructure and PAPER Move:  \$208k
	\item limited upgrade to PAPER electronics:  \$30k
\end{itemize}
\item {\em Year 2:}  HERA-127 construction
\begin{itemize}
	\item antenna components, sub-assemblies and installation:  \$775k
	\item node fabrication and installation:  \$192k
	\item site infrastructure:  \$153k
	\item limited correlator upgrade:  \$38k
	\item monitor and control:  \$30k
\end{itemize}
\item {\em Year 3:}  HERA-331 construction
\begin{itemize}
	\item antenna components, sub-assemblies and installation:  \$1,268k
	\item node fabrication and installation:  \$314k
	\item correlator:  \$152k
	\item monitor and control:  \$30k
\end{itemize}
\item {\em Year 4:}  HERA-568 construction
\begin{itemize}
	\item antenna components, sub-assemblies and installation:  \$1,479k
	\item node fabrication and installation:  \$366k
	\item correlator:  \$191k
	\item monitor, control and storage:  \$30k
\end{itemize}
\item {\em Year 5:}  Operations
\begin{itemize}
	\item storage:  \$30k
\end{itemize}

\end{itemize}

{\bf Travel:} We request \$104k for domestic and foreign travel support, consisting of airfare, lodging, and per diem for (a) domestic team meetings, (b) one conference per person per year and (c) travel to the South African site for more extensive periods for a subset of the team.

{\bf Materials and Supplies:}  Funds are requested for the following miscellaneous expenses over five years.
\begin{itemize}
\item Page charges (\$5k): \$1000/yr over five years
\item Licenses (\$17k):  \$3500/yr over five years
\item Computers (\$5k):  \$5000 in year 1
\item Laboratory materials (\$15k):  \$5000/yr over first three years
\item Shipping of equipment to South Africa:  (\$175k):  \$10k, \$35k, \$65k, \$65k
\end{itemize}

{\bf Indirect Costs:}
The rate of 56.5\% is used to determine the estimated Indirect Cost. The total indirect cost is calculated using the modified total direct cost base (which excludes equipment, graduate student tuition and fees). This reflects the On-Campus Organized Research Facilities and Administrative Cost Rate established by the institution and DHHS in an agreement dated 27 July 2007.
\end{document}