\documentclass[preprint]{aastex}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{mdwlist}
\usepackage{natbib}
\usepackage{natbibspacing}
\setlength{\bibspacing}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\footnotesep}{8pt}
\pagestyle{empty}

%Project Summary. (1 page maximum) Required elements include an overview of the
%proposed program, and separate entries addressing the intellectual merit and
%broader impacts. The summary should be written in the third person, informative
%to those working in the same or related field(s), and understandable to a
%scientifically or technically literate reader.

\begin{document}
\pagestyle{empty}

\title{HERA: Illuminating Our Early Universe}

\section*{Overview}
%Overview: Insert a self-contained description of the activity that would result if the proposal were funded and include a statement of objectives and methods to be employed. 

Hydrogen Epoch of Reionization Arrays (HERA) is a roadmap for characterizing
cosmic reionization --- the epoch when the first luminous sources ionized the
bulk of the hydrogen in the Universe --- via redshifted 21~cm hyperfine
emission from neutral hydrogen.  Building on the successes of first-generation
HERA instruments (PAPER, MWA, LEDA, MITEoR, and EDGES), we propose to a staged
build-out to the next phase of HERA: a 568-element radio interferometric array
of 14-m parabolic dishes observing between 50 and 225 MHz.  This
instrument brings to bear both experimentally validated
foreground suppression techniques and the collecting area required to open new windows into our early
universe.  New measurements with HERA-568 will be capable of determining
ionization fraction versus redshift over the bulk of reionization,
constraining the size of ionization bubbles to help determine the properties of
first galaxies, and directly imaging larger structures during
reionization.  HERA will also begin to explore the `dark ages' before 
reionization when a wealth of astrophysical and cosmological processes
impacted the temperature of the intergalactic medium.

\section*{Intellectual Merit}
%Intellectual Merit: Describe the potential of the proposed activity to meet the Intellectual Merit criterion

The 21~cm hyperfine transition is widely recognized as potentially the most
powerful probe of large-scale structure from the dark ages through
reionization.  The evolution of this signal from the neutral intergalactic
medium depends on myriad physical processes; the relative importance of
these competing effects is sensitive to, among other things, the expansion of
the universe, the ignition of the first stars and galaxies, the formation of
the first massive black holes, and the relative
velocity of baryonic matter and dark-matter halos.
Detecting this signal will have an impact
comparable to the discovery of the cosmic microwave background, and study of the three-dimensional
evolution of large-scale structure via the 21~cm line has the
potential to become `the richest of all cosmological data sets'.

Given these complexities, current constraints on cosmic reionization remain rudimentary. When did it
occur, and over what timescale?  What objects dominated the radiation field?
How were the objects distributed? Did the first generation of stars \& galaxies
enhance or suppress the formation of subsequent stars \& galaxies in the
original halo and smaller nearby halos? Without new constraints, further
progress on theoretical modeling of first galaxy formation and cosmic
reionization remains problematic.  The proposed HERA program provides a
powerful new tool for producing observational constraints on reionization, and
potentially on large scale structure evolution during the dark ages.  The new
windows that HERA opens into our early universe have the capability to
transform our scientific understanding of our cosmic dawn at the complex intersection of cosmology
and astrophysics.  HERA represents a major step toward unlocking the widely recognized scientific potential of
21~cm cosmology.

\section*{Broader Impacts}
%Broader Impacts: Describe the potential of the proposed activity to meet the Broader Impacts criterion

This proposal addresses the loss of talented astronomers involved in
instrumentation by addressing a gap in preparation between the undergraduate
and graduate level of involvement.  Young graduate students will be involved
in the the development,
deployment, commissioning, and characterization of all stages of the HERA
instrument. This proposal also funds an intern
position at UC Berkeley's RAL, offered each year to a person to gain
practical experience developing
the HERA instrument, with the goal of acquiring the skills required for
pursuing graduate research in instrumentation.

Another important HERA activity, and
one of the most personally fulfilling, is the cooperative education of
under-served students from South Africa in STEM fields.
We have established formal collaborations
with faculty at South African universities to engage doctoral students in all aspects of the HERA project, from
field engineering to rigorous data analysis. We also plan to establish
student exchanges to draw
diverse students from South Africa into many of HERA's funded graduate positions.
Involvement in the
program will help ensure that these students are well-positioned for
future success.

Finally, HERA will disseminate various data products to the community,
including wide-field sky maps, high-speed continuum images, deep
foreground-subtracted images, and full-sensitivity data products, for enabling
additional science and for cross-correlation analyses with other large-scale
probes of the early universe.

\end{document}
