\documentclass[preprint]{aastex} 

\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\footnotesep}{8pt}
\pagestyle{empty}

\newcommand{\role}[3]{\noindent{\bf #1} ({\em #2}):  #3\vspace{0.15in}}

\begin{document}
\title{Supplementary Document:  Project Personnel}

\noindent

\noindent
The following named team members are major contributors to the project.
\vspace{0.25in}

\role{James Aguirre}{University of Pennsylvania}{Prof. Aguirre will develop algorithms for power spectrum analysis and lead the data storage task.  Aguirre brings to bear his expertise in power spectrum and polarization analysis from PAPER.}

\role{Gianni Bernardi}{South Africa SKA Project}{Dr. Bernardi will be a key South African contributor to the foreground and power spectrum analysis.}

\role{Judd Bowman}{Arizona State University}{Prof. Bowman will lead the system calibration task, based on extensive experience with EDGES and MWA.  Bowman will participate in furthering the imaging and imaging power spectrum analysis.}

\role{Richard Bradley}{National Radio Astronomy Observatory}{Dr. Bradley will serve as the chief analog architect based on his extensive experience at NRAO, particularly in designing and fabricating the entire PAPER analog signal path.}

\role{Chris Carilli}{National Radio Astronomy Observatory}{Dr. Carilli will develop algorithms for image-based science and lead student efforts in obtaining other science from the telescope..}

\role{David DeBoer} {University of California Berkeley}{Dr. DeBoer is the Project Manager and also serves as design engineer for the overall system and antenna.  He will oversee the design, construction and operational phases of the project.  }

\role{Steve Furlanetto}{University of California Los Angeles}{Dr. Furlanetto will develop theoretical frameworks for the project.}

\role{Robert Goeke}{Massachusetts Institute of Technology}{Mr. Goeke will serve as the Project Engineer and will oversee the component-level design and fabrication of the antenna.}

\role{Jacqueline Hewitt}{Massachusetts Institute of Technology}{Prof. Hewitt will lead the data archive task.}

\role{Daniel Jacobs}{Arizona State University}{Dr. Jacobs will develop pipelines for power spectrum and develop user monitor and command systems.}

\role{Adam Lidz}{University of Pennsylvania}{Dr. Lidz will help develop the theoretical framework within which to analyze the power spectrum data.}

\role{Adrian Liu}{University of California Berkeley}{Dr. Liu will develop algorithms for power spectrum analysis.}

\role{Matthew McQuinn}{University of Washington}{Dr. McQuinn will help develop the theoretical framework within which to analyze the power spectrum data.}

\role{Andrei Mesinger}{Scuola Normale Superiore}{Prof. Mesinger will develop fast, semi-numeric algorithms for generating mock power spectra that can be compared to measured data for astrophysical and cosmological parameter extraction.}

\role{Miguel Morales}{University of Washington}{Prof. Morales will develop power spectrum algorithms and perform analysis.  He will lead the monitor and command database software effort.}

\role{Aaron Parsons}{University of California Berkeley}{Prof. Parsons will serve as the Principal Investigator for the award.  He is the Project Director and will also develop power spectrum algorithms and pipelines and perform analysis.  He will lead the data compression task.}

\role{Max Tegmark}{Massachusetts Institute of Technology}{Prof. Tegmark will lead the research and development task developing algorithms for efficient direct-imaging methods.}

\role{William Walbrugh}{South Africa SKA Project}{Mr. Walbrugh will continue to be the SKA-SA liaison to the project.}

\role{Dan Werthimer}{University of California Berkeley}{Mr. Werthimer will serve as the chief digital architect and lead the digital processing task.}



\end{document}
